\section{Background}

\subsection{Remote Pair Programming}

Remote Pair Programming tool (RPP) is a tool that serves  to coordinate how two programmers or researchers work together. The  adoption of RPP has emerged a lot  in academic environments where students that  were used to work alone, could finally work in a group on a given task  independently on their own computers for the same problem and converge at the end to compare solutions.  RPP is the best way to learn stuff and eliminating many of the technical challenges that often appears among developers. In fact, developers with more experience acts as navigator while the less experienced developer will act as driver while communicating and discussing remotely on the same document[4]. 

\subsection{Data Encryption Standard}

Data Encryption is a method to hide and secure data. In this project the Data Encryption Standard (DES), or Triple DES are used to encrypt data in communication[6]. DES is an encryption standard based on block cipher encryption, where a Key is used to cipher a data block which then can be deciphered. Triple DES is a three step encryption, where three keys are used to decipher a data block. This will be more covered in the Secure Encryption section. 
The remote pair programming was introduced in order to help two people or a team of coworkers working on the same task, trying to solve it as unit while  by sharing knowledge for each other. By this approach, it means that one person have an idea in mind, share it in open document to the other person. The other person acts as an observer while studying what his partner is sharing. Thereafter, both persons will have discussion which will lead for the solution of their task they were looking for. 
